Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-03-23 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Minor editing to Madrzykowski references.

The vertical radiant panel is used as documented in ASTM~E162 and normally provides a measure of downward, opposed-flow flame spread~\cite{ASTME162}.  The apparatus measures the surface flammability of materials using a pre-mixed air-gas-fired radiant panel that is 305~mm × 457~mm.

>>>>

The vertical radiant panel is used as documented in ASTM~E162 and normally provides a measure of downward, opposed-flow flame spread~\cite{ASTM_E162}.  The apparatus measures the surface flammability of materials using a pre-mixed air-gas-fired radiant panel that is 305~mm by 457~mm.
